\chapter*{Dedication}

To my parents, José Manuel and Maria de Lurdes Fonseca. Thank you for your
unwavering love, support, encouragement and patience. Thank you for instilling
in me a love for learning and values that will stay with me for a lifetime.
This thesis is dedicated to you with the deepest love and gratitude.  I hope
it will make you as proud as I am to be your son.

\chapter*{Acknowledgements}

I would like to thank MIT Portugal for the financial support provided
throughout the PhD programme. My adviser, Professor Fernando Bação, PhD, for
all the guidance offered over these years. Georgios Douzas, PhD, for the
multiple discussions, tips and help on technical challenges faced throughout
the research work. Manuel Rodrigues for proofreading multiple chapters of this
dissertation.

I would like to express my deepest gratitude to my family for their unwavering
support and encouragement throughout my academic journey. Their love,
patience, and sacrifice have sustained me during the most challenging times. I
could not have come this far without them. I am especially grateful to my
parents, José Manuel and Maria de Lurdes, my siblings, Hugo and Inês, my
brother-in-law, Hugo and my grandmother, Teresa. 

I would also like to express my deep gratitude to Yasmina El Fassi. Her
understanding, love and support were essential to overcome the 
challenges faced throughout the program.

I am lucky to have had the support and encouragement of many friends
throughout my academic journey. I would like to take this opportunity to
extend my heartfelt gratitude to the following friends who have been there for
me in every step of the way: Andrew Bell, Ana Correia, Ana Vieira, Francisco
Braga, Francisco Martins, Margarida Saragoça, Manvel Khudinyan, Maria Reyes,
Miguel Meco, Miguel Portas, Oumaima Derfoufi, Pedro Rodrigues and Rafaela
Henriques.

During my time in the PhD program, I had the opportunity to meet an
outstanding group of friends and colleagues. Sharing this experience with them
made this journey truly special. I would like to express my sincere thanks to
Professor Marco Painho and my friends Darina Vorobeva, Maria Anastasiadou and
Vicente Tang.

I would also like to thank my secondary school biology teacher, Regina Lucena.
Her passion for the subject and dedication to her students have had a profound
impact on me. Her teachings not only inspired me to pursue a career in
science, but also instilled in me a deep sense of curiosity that I will carry
with me for the rest of my life. I will always be grateful for the way she
challenged and encouraged me.

Finally, I would like to thank my cats, Tom and Kika, for keeping me company
through the writing of most of this dissertation.
