\chapter*{Publication list}

The following papers have been published (or submitted) as a result of this
dissertation:

\begin{itemize}

    \item Fonseca, J., Bacao, F. (2023). Geometric SMOTE for Imbalanced
        Datasets with Nominal and Continuous Features. Submitted to Expert
        Systems with Applications (waiting for 2nd set of reviews).

    \item Fonseca, J., Bacao, F. (2023). Tabular and Latent Space Synthetic
        Data Generation: A Literature Review. Submitted to Journal of Big
        Data (waiting for 2nd set of reviews).

    \item Fonseca, J., Bacao, F. (2023). Improving Active Learning
        Performance through the Use of Data Augmentation. International
        Journal of Intelligent Systems, 2023.
        https://doi.org/10.1155/2023/7941878

    \item Fonseca, J., Douzas, G., Bacao, F. (2021). Increasing the
        Effectiveness of Active Learning: Introducing Artificial Data
        Generation in Active Learning for Land Use/Land Cover Classification.
        Remote Sensing, 13(13), 2619.  https://doi.org/10.3390/rs13132619

    \item Fonseca, J., Douzas, G., Bacao, F. (2021). Improving Imbalanced Land
        Cover Classification with K-Means SMOTE: Detecting and Oversampling
        Distinctive Minority Spectral Signatures. Information, 12(7), 266.
        https://doi.org/10.3390/info12070266

\end{itemize}

The research outputs below were developed during the programme, although
not included in this dissertation. They are either intermediate work or
unrelated to the topic of the thesis:

\begin{itemize}

    \item Fonseca, J., Bell, A., Abrate, C., Bonchi, F., Stoyanovich, J.
        (2023). Setting the Right Expectations: Algorithmic Recourse Over
        Time. Submitted to the 3rd ACM conference on Equity and Access in
        Algorithms, Mechanisms, and Optimization (EAAMO'23).

    \item Fonseca, J., Bacao, F. (2022). Research trends and applications of
        data augmentation algorithms. arXiv preprint arXiv:2207.08817.
        https://arxiv.org/abs/2207.08817

    \item Crayton, A., Fonseca, J., Mehra, K., Ng, M., Ross J.,
        Sandoval-Castañeda, M., von Gnecht, R. (2021). Narratives and Needs:
        Analyzing Experiences of Cyclone Amphan Using Twitter Discourse, in
        IJCAI 2021 Workshop on AI for Social Good.
        https://crcs.seas.harvard.edu/publications/narratives-and-needs-analyzing-experiences-cyclone-amphan-using-twitter-discourse

\end{itemize}
