\chapter{%
    Tabular and Latent Space Synthetic Data Generation: A Literature Review
}~\label{chp:synthetic-data-review}
\graphicspath{{figures/synthetic-data-review/}}

\begin{adjustwidth}{30pt}{30pt}

    The generation of synthetic data can be used for anonymization,
    regularization, oversampling, semi-supervised learning, self-supervised
    learning, and several other tasks. Such broad potential motivated the
    development of new algorithms, specialized in data generation for specific
    data formats and Machine Learning (ML) tasks. However, one of the most
    common data formats used in industrial applications, tabular data, is
    generally overlooked; Literature analyses are scarce, state-of-the-art
    methods are spread across domains or ML tasks and there is little to no
    distinction among the main types of mechanism underlying synthetic data
    generation algorithms. In this paper, we analyze tabular and latent space
    synthetic data generation algorithms. Specifically, we propose a unified
    taxonomy as an extension and generalization of previous taxonomies, review
    70 generation algorithms across six ML problems, distinguish the main
    generation mechanisms identified into six categories, describe each type
    of generation mechanism, discuss metrics to evaluate the quality of
    synthetic data and provide recommendations for future research. We expect
    this study to assist researchers and practitioners identify relevant gaps
    in the literature and design better and more informed practices with
    synthetic data.

\end{adjustwidth}

\vspace{.5cm}
\textbf{Keywords:} Synthetic Data; Data Augmentation; Oversampling;
Regularization; Privacy

\input{chapters/2-synthetic-data-review-sections/introduction.tex}
\input{chapters/2-synthetic-data-review-sections/background.tex}
\input{chapters/2-synthetic-data-review-sections/taxonomy.tex}
\input{chapters/2-synthetic-data-review-sections/applications.tex}
\input{chapters/2-synthetic-data-review-sections/generation-mechanisms.tex}
\input{chapters/2-synthetic-data-review-sections/evaluating-quality-of-synthetic-data.tex}
\input{chapters/2-synthetic-data-review-sections/discussion.tex}
\input{chapters/2-synthetic-data-review-sections/future-work.tex}
\input{chapters/2-synthetic-data-review-sections/conclusions.tex}

\textbf{This chapter was published as:} Fonseca, J., Bacao, F. (2023). Tabular
and latent space synthetic data generation: a literature review. Journal of
Big Data, 10(1), 115.  https://doi.org/10.1186/s40537-023-00792-7
